### 2019-04-15 VG500/HW5/submission.tex
add ex5

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{enumerate}
\usepackage{ulem} 
\usepackage{pdfpages}
\usepackage{multirow}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

@@

\section{Group exercise}

>>>>

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{enumerate}
\usepackage{ulem} 
\usepackage{pdfpages}
\usepackage{multirow}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{listings}
\lstset{language=Matlab}
\usepackage{hyperref}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

@@

\section{Group exercise}
	In the traditional method of two round-trip secure search, the trapdoors of each keyword list are generated by the data owner or his agent, and then the user will search them. This will be a time-consuming job for mobile device and significantly degrade the user experience. In our method, each trapdoor can be generated by its own device.\newline
	The user terminal stores the noise set and a frequently-used cache. The cache originally stores the keywords which are commonly used in the corpus and corresponding feature bits. If the user inputs a keyword, it will do the stemming process first, and then search the cache. If finding the keyword, it will return the intermediate trapdoor immediately, otherwise it will calculate the feature bits and add the keyword to the cache for next time use. The whole process is presented in Fig. 4. By introducing cache, the time of generating trapdoors can be efficiently reduced.
